---
title: "MAPBIOMAS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MAPBIOMAS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## The Dataset

The MAPBIOMAS project gathers data reporting the type of land covering each year by area, that is, for example, the area used for a temporary crop of soybeans. It also reports the transition between coverings during given years.

The cover levels inform the usage of the refered land. The levels range from the least to the most specific information about the land.
Example: level_0: Anthropic | level_1: Farming | level_2: Agriculture | level_3: Temporary Crops

The data available has an yearly frequency and is available starting from the year 1989.

## Usage
Using the function is easy enough:

```{r, eval=FALSE}
library(datazoom.amazonia)

# download treated Mapbiomas Cover data in english
data = load_mapbiomas(dataset = "mapbiomas_cover", raw_data = FALSE, time_period = "all",
                      language = "eng")

# download treated Mapbiomas Transition data in portuguese
data = load_mapbiomas(dataset = "mapbiomas_transition", raw_data = FALSE, time_period = "all",
                      language = "pt")

# download treated Mapbiomas Grazing Quality data in portuguese
data = load_mapbiomas(dataset = "mapbiomas_grazing_quality", raw_data = FALSE, time_period = "all", language = "pt")

# download treated Mapbiomas Irrigation data in english

data = load_mapbiomas(dataset = "mapbiomas_irrigation", raw_data = FALSE, time_period = "all", language = "eng")

# download treated Mapbiomas deforestauon/regeneration data in portuguese

data = load_mapbiomas(dataset = "mapbiomas_deforestation_regeneration", raw_data = FALSE, time_period = 2011, language = "eng")
```
